%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.69in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% allow utf-8
\usepackage[utf8]{inputenc}

% allows enumerate alphabets
\usepackage{enumitem}
% Makes resume-specific commands available.
\usepackage{resume}
\usepackage{footmisc}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
{\centering
\maintitle{Complete list of publications of David Koppstein}{}{}\par
}
\nobreakvspace{0.1em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\vspace{0.05in}

%
\begin{enumerate}[label=\large{\textbf{\Alph*)}}]

\item {\large\textbf{Publications with peer review process}}

\begin{enumerate}[label=\arabic*.]
{\item Rizzetto S, \textbf{Koppstein D}, Samir J, Singh M, Reed JH, Cai CH, Lloyd AR, Eltahla AA, Goodnow CC, Luciani F. B-cell receptor reconstruction from single-cell RNA-seq with VDJPuzzle. 2018. \textit{Bioinformatics. doi:10.1093/bioinformatics/bty203}}.
{\item Grüning B, Dale R, Sjödin A, Chapman BA, Rowe J, Tomkins-Tinch CH, Valieris R, Koster J, \textbf{The Bioconda Team}. Bioconda: sustainable and comprehensive software distribution for the life sciences. 2018. \textit{Nature Methods 15, 475-76}.}
{\item \textbf{Koppstein D}, Ashour J, and Bartel DP. Sequencing the cap-snatching repertoire of H1N1
influenza provides insight into the mechanism of viral transcription initiation. 2015. \textit{Nucleic Acids Research 43(10), 5052-5064}.}
{\item Hezroni H, \textbf{Koppstein D}, Schwartz M, Tabin CJ, Bartel DP, and Ulitsky I. 2015. Principles of long noncoding
RNA evolution derived from direct comparison of transcriptomes in 14 vertebrates. \textit{Cell Reports 11(7), 1110-1122}}.
{\item Nam J-W, Rissland OS, \textbf{Koppstein D}, Abreu-Goodger C, Jan CH, Agarwal V, Yildirim, Rodriguez A, and Bartel DP. 2014. Global Analyses of the Effect of Different Cellular Contexts on MicroRNA Targeting. \textit{Molecular Cell. 53, 1031-1043.}}
{\item Ulitsky I, Shkumatava A, Jan C, Subtelny AO, \textbf{Koppstein D}, Bell G, Sive H, and Bartel DP. 2012. Extensive alternative polyadenylation during zebrafish development. \textit{Genome Research. 22(10):2054-66.}}
{\item Agarwal A\footnote[1]{Authors contributed equally to this publication.}, \textbf{Koppstein D}\footnotemark[1], Rozowsky J, Sboner A, Habegger L, Hillier LW, Sasidharan R, Reinke V, Waterston RH, and Gerstein M. 2010. Comparison and calibration of transcriptome data from RNA-Seq and tiling arrays. \textit{BMC Genomics. 11:383.}}
{\item Mukhopadhyay J, Das K, Ismail S, \textbf{Koppstein D}, Jang M, Hudson B, Sarafianos S, Tuske S, Patel J, Jansen R, Irschik H, Arnold E, and Ebright RH. 2008. Myxopyronin, Corallopyronin, and Ripostatin Inhibit Transcription by Binding to the RNA Polymerase Switch Region. \textit{Cell. 135:295-307.}}
\end{enumerate}

% publisher's acknowledgment of receipt enclosed
\item {\large\textbf{Submitted publications with peer review process}}

\begin{enumerate}[label=\arabic*.]
\item Grigaityte K, Carter JA, Goldfless SJ, Jefferey EW, Hause RJ, Jiang Y, \textbf{Koppstein D}, Briggs AW, Church GM, Vigneault F, Atwal GS. Single-cell sequencing reveals $\alpha \beta$ chain pairing shapes the T cell repertoire. 2017. \textit{bioRxiv}. Submitted to Science Immunology (publisher's acknowledgment of receipt enclosed).
\end{enumerate}

{\item {\large\textbf{Publications without peer review process}}}

\begin{enumerate}[label=\arabic*.]
{\item Briggs AW, Goldfless SJ, Timberlake S, Belmont BJ, Clouser CR, \textbf{Koppstein D}, Sok D, Vander Heiden JA, Tamminen MV, Kleinstein SH, Burton DR, Church GM, Vigneault F. 2017. Tumor-infiltrating immune repertoires captured by single-cell barcoding in emulsion. \textit{bioRxiv}.}
\end{enumerate}

\end{enumerate}

{\large\textbf{The following above mentioned publications have evolved from my doctoral dissertation: A3, A5, A6}}

\end{document}
