%
% LaTeX source of my resume
% =========================
%
% Heavily commented to to fit even LaTeX beginners (hopefully).
%
% See the `README.md` file for more info.
%
% This file is licensed under the CC-NC-ND Creative Commons license.
%


% Start a document with the here given default font size and paper size.
\documentclass[10pt,a4paper]{article}

% Set the page margins.
\usepackage[a4paper,margin=0.69in]{geometry}

% Setup the language.
\usepackage[english]{babel}
\hyphenation{Some-long-word}

% allow utf-8
\usepackage[utf8]{inputenc}

% Makes resume-specific commands available.
\usepackage{resume}
\usepackage{footmisc}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}  % begin the content of the document
\sloppy  % this to relax whitespacing in favour of straight margins


% title on top of the document
\maintitle{DAVID N.P. KOPPSTEIN}{}{}

\nobreakvspace{0.1em}  % add some page break averse vertical spacing

% \noindent prevents paragraph's first lines from indenting
% \mbox is used to obfuscate the email address
% \sbull is a spaced bullet
% \href well..
% \\ breaks the line into a new paragraph
\noindent\href{mailto:david.koppstein@gmail.coml}{david.koppstein\mbox{}@\mbox{}gmail.com}\sbull
\textsmaller{}+49 170 7740947 \sbull Skype: david.koppstein
\vspace{0.05in}

\spacedhrule{-0.2em}{-0.6em}

\roottitle{Education}

\headedsection
  {Massachusetts Institute of Technology}
  {\textsc{Cambridge, MA}} {%
  \headedsubsection
    {\textnormal{Ph.D, Biology}}
    {2015} {}
}

\headedsection
  {Yale University}
  {\textsc{New Haven, CT}} {%
  \headedsubsection
    {\textnormal{B.S., Molecular Biophysics and Biochemistry}}
    {2008} {}
}
\vspace{0.05in}

\spacedhrule{-0.2em}{-0.6em}

\roottitle{Experience}

\headedsection  % sets the header for the section and includes any subsections
  {Nikolaus Rajewsky Lab, Max Delbrück Center for Molecular Medicine}
  {\textsc{Berlin, Germany}} {%
  \headedsubsection
    {Postdoctoral Researcher}
    {June \apo18 -- present}
    {\bodytext{Investigating the function of alternative RNA isoforms during differentiation of neural lineages in the context of neurodegenerative disease. Mentoring one Masters student. }}
}

\headedsection  % sets the header for the section and includes any subsections
  {Viral Immunology Systems Program, Kirby Institute, UNSW}
  {\textsc{Sydney, Australia}} {%
  \headedsubsection
    {Postdoctoral Researcher}
    {Apr \apo17 -- April \apo18}
    {\bodytext{Developed computational methods for analyzing single-cell transcriptomics data of immune cells. Mentored two Ph.D students, a Masters student, and an Honors student. }}
}

\headedsection  % sets the header for the section and includes any subsections
  {Juno Therapeutics}
  {\textsc{Seattle, WA, USA}} {%
  \headedsubsection
    {Data Scientist}
    {Jan \apo16 -- Mar \apo17}
    {\bodytext{Analyzed and communicated immunosequencing analyses for internal projects and external academic collaborators. Conducted analyses for internal RNA-seq and vector integration profiling projects. Served as interim manager of the data science team. }}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {AbVitro}
  {\textsc{Boston, MA, USA}} {%
  \headedsubsection
    {Data Scientist}
    {Mar \apo15 -- Dec \apo15}
    {\bodytext{Designed bioinformatics pipeline for single-cell immunosequencing. Mined receptor sequences from tumor-infiltrating lymphocytes and nominated candidates for screening. \textit{(Acquired by Juno Therapeutics).}}}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {David Bartel Lab, MIT}
  {\textsc{Boston, MA, USA}} {%
  \headedsubsection
    {Graduate Student}
    {May \apo10 -- Mar \apo15}
    {\bodytext{Designed, implemented, and analyzed high-throughput sequencing experiments using the Illumina platform to investigate influenza's cap-snatching repertoire. Utilized 3P-seq to precisely examine alternative cleavage and polyadenylation in diverse genetic backgrounds and model organisms.}}
}

\headedsection  % sets the header for a subsection and contains usually body text
  {Joan Steitz Lab, Yale}
  {\textsc{New Haven, CT, USA}} {%
  \headedsubsection
    {Undergraduate Student}
    {May \apo06 -- Apr \apo08}
    {\bodytext{Investigated the function of Herpesvirus saimiri Small U RNAs (HSURs).}}
}

\spacedhrule{0.9em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Publications and Preprints}  % a root section title
{\noindent Wyler M, Mösbauer K, Franke F, Diag A, Gottula LT, Arsie R, Klironomos F, \textbf{Koppstein D}, ..., Rajewsky N, Drosten C, Landthaler M. Bulk and single-cell gene expression profiling of SARS-CoV-2 infected human cell lines identifies molecular targets for therapeutic intervention. 2020. \textit{Accepted Cell. Rep.}. \vspace{0.5em} \\
{\noindent Singh M, Jackson KJL, Wang JJ, Schofield P, Field MA, \textbf{Koppstein D}, ..., Luciani F, Gordon TP, Goodnow CC, Reed JH. Lymphoma driver mutations in the pathogenic evolution of an iconic human autoantibody. 2020. \textit{Cell. doi:10.1016/j.cell.2020.01.029}. \vspace{0.5em} \\
{\noindent Rizzetto S, \textbf{Koppstein D}, Samir J, Singh M, Reed JH, Cai CH, Lloyd AR, Eltahla AA, Goodnow CC, Luciani F. B-cell receptor reconstruction from single-cell RNA-seq with VDJPuzzle. 2018. \textit{Bioinformatics. doi:10.1093/bioinformatics/bty203}. \vspace{0.5em} \\
{\noindent Grüning B, Dale R, Sjödin A, Chapman BA, Rowe J, Tomkins-Tinch CH, Valieris R, Koster J, \textbf{The Bioconda Team}. Bioconda: sustainable and comprehensive software distribution for the life sciences. 2018. \textit{Nature Methods 15, 475-76}.} \vspace{0.4em} \\
{\noindent Grigaityte K, Carter JA, Goldfless SJ, Jefferey EW, Hause RJ, Jiang Y, \textbf{Koppstein D}, Briggs AW, Church GM, Vigneault F, Atwal GS. Single-cell sequencing reveals $\alpha \beta$ chain pairing shapes the T cell repertoire. 2017. \textit{bioRxiv}.} \vspace{-0.8em} \\
{\noindent Briggs AW, Goldfless SJ, Timberlake S, Belmont BJ, Clouser CR, \textbf{Koppstein D}, Sok D, Vander Heiden JA, Tamminen MV, Kleinstein SH, Burton DR, Church GM, Vigneault F. 2017. Tumor-infiltrating immune repertoires captured by single-cell barcoding in emulsion. \textit{bioRxiv}. \vspace{0.5em} \\
{\noindent \textbf{Koppstein D}, Ashour J, and Bartel DP. Sequencing the cap-snatching repertoire of H1N1
influenza provides insight into the mechanism of viral transcription initiation. 2015. \textit{Nucleic Acids Research 43(10), 5052-5064}.} \vspace{0.5em} \\
{\noindent Hezroni H, \textbf{Koppstein D}, Schwartz M, Tabin CJ, Bartel DP, and Ulitsky I. 2015. Principles of long noncoding
RNA evolution derived from direct comparison of transcriptomes in 14 vertebrates. \textit{Cell Reports 11(7), 1110-1122}}. \vspace{0.5em} \\
{\noindent Nam J-W, Rissland OS, \textbf{Koppstein D}, Abreu-Goodger C, Jan CH, Agarwal V, Yildirim, Rodriguez A, and Bartel DP. 2014. Global Analyses of the Effect of Different Cellular Contexts on MicroRNA Targeting. \textit{Molecular Cell. 53, 1031-1043.}} \vspace{0.5em} \\
{\noindent Ulitsky I, Shkumatava A, Jan C, Subtelny AO, \textbf{Koppstein D}, Bell G, Sive H, and Bartel DP. 2012. Extensive alternative polyadenylation during zebrafish development. \textit{Genome Research. 22(10):2054-66.}} \vspace{0.5em} \\
{\noindent Agarwal A\footnote[1]{Authors contributed equally to this publication.}, \textbf{Koppstein D}\footnotemark[1], Rozowsky J, Sboner A, Habegger L, Hillier LW, Sasidharan R, Reinke V, Waterston RH, and Gerstein M. 2010. Comparison and calibration of transcriptome data from RNA-Seq and tiling arrays. \textit{BMC Genomics. 11:383.}} \vspace{0.3em} \\
{\noindent Mukhopadhyay J, Das K, Ismail S, \textbf{Koppstein D}, Jang M, Hudson B, Sarafianos S, Tuske S, Patel J, Jansen R, Irschik H, Arnold E, and Ebright RH. 2008. Myxopyronin, Corallopyronin, and Ripostatin Inhibit Transcription by Binding to the RNA Polymerase Switch Region. \textit{Cell. 135:295-307.}} \vspace{0.3em} \\

\spacedhrule{0.1em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Presentations and Posters}

{\noindent \textbf{Koppstein D}, Rizzetto S, Samir J, Singh M, Reed JH, Cai CH, Lloyd AR, Eltahla AA, Goodnow CC, Luciani F. VDJPuzzle: A computational method for BCR and TCR reconstruction from single-cell sequencing data. Australian Bioinformatics And Computational Biology Society. Oral presentation delivered in Adelaide, Australia, November 2017.} \vspace{-0.8em} \\

{\noindent \textbf{Koppstein D} Rizzetto S, Samir J, Singh M, Reed JH, Cai CH, Lloyd AR, Eltahla AA, Goodnow CC, Luciani F. VDJPuzzle: A computational method for BCR and TCR reconstruction from single-cell sequencing data. Australian Cellular Panomics Consortium. Poster presentation delivered in Melbourne, Australia, November 2017.} \vspace{-0.8em} \\

{\noindent \textbf{Koppstein D}, Rizzetto S, Samir J, Singh M, Reed JH, Cai CH, Lloyd AR, Eltahla AA, Goodnow CC, Luciani F. VDJPuzzle: A computational method for BCR and TCR reconstruction from single-cell sequencing data. Australian Society for Immunology. Oral presentation delivered in Bowral, Australia, November 2017.} \vspace{-0.8em} \\

{\noindent \textbf{Koppstein D}, Ashour J, Bartel D. Quantitative assessment of influenza's cap-snatching repertoire by RNA sequencing. RNA Society. Poster presentation delivered in Quebec City, Canada, June 2014.}

\spacedhrule{1.3em}{-0.4em}  % a horizontal line with some vertical spacing before and after

\roottitle{Skills}  % a root section title

  % special section that has an inline header with a 'hanging' paragraph
\headedsection{Wet lab}
{\bodytext{Extensive experience with Illumina library preparation and custom design: 3P-Seq, SMART-seq, and standard RNA-seq. Experience running single-cell 10X Chromium. Experience with molecular cloning, tissue culture, Northern/Western blots, protein purification, PCR, and yeast genetics.}
}

\vspace{-0.3em}

\headedsection{Dry lab}
{\bodytext{Fluent in Python and R. Expertise with modern bioinformatics tools including samtools, STAR, featureCounts, edgeR, Picard, etc. Experience with analysing single-cell sequencing data using scater, Seurat, etc. Experience writing scalable computational pipelines using Snakemake. Experience with statistical methods and machine learning techniques. Experience managing a team of computational biologists using agile methods.} \vspace{-0.2em}
}

\vspace{0.1in}

\spacedhrule{0.1em}{-0.2em}  % a horizontal line with some vertical spacing before and after

\roottitle{Fellowships and Awards}  % a root section

\begin{itemize}
\item Juno CEO Award for Outstanding Performance, 2016
\item NSF Graduate Research Fellowship Program, Honorable Mention, 2011
\item Yale STARS II Research Fellowship, 2007-8
\end{itemize}

\spacedhrule{0.4em}{-0.2em}  % a horizontal line with some vertical spacing before and after

\roottitle{Extracurricular}

\begin{itemize}
\item Urban Cycling Skills and Safety Clinic Organizer, 2013-4
\item Whitehead Partner for High School Science Teacher Outreach, 2012
\item MIT Cycling Team Officer, 2012-2014
\end{itemize}

\end{document}
